Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-06-25 vesicle_code/docs/adhesion/adhesion.tex
worked on revisions

We characterize the effect of the Hamaker constant and shear rate by
determining a critical Hamaker constant, $\mathcal{H}_c$, which
determines if the vesicles form a doublet or separate.  We fix the
separation distance to $\delta = 0.4$ and the vesicle reduced area to
$\Delta A = 0.9$.  In
Figure~\ref{fig:sflow_distance}(a), we plot the minimum distance
between the vesicles as a function of time for various Hamaker
constants.  The red curves correspond to Hamaker constants that are too
small to bind the vesicles into a doublet, and the blue curves
correspond to Hamaker constants that are sufficiently large to form a
doublet.  In Figure~\ref{fig:sflow_distance}(b), we plot the time
required for the doublet to make a complete revolution at a variety of
Hamaker constants and shear rates.  For a fixed Hamaker contant, as
expected, the period decreases for larger shear rates.  In addition, for
a fixed shear rate, the period decreases as the Hamaker constant
increases, but the period eventually plateaus.

>>>>

We characterize the effect of the Hamaker constant and shear rate by
determining a critical Hamaker constant, $\mathcal{H}_c$, which
determines if the vesicles form a doublet or separate.  We fix the
separation distance to $\delta = 0.4$ and the vesicle reduced area to
$\Delta A = 0.9$.  In
Figure~\ref{fig:sflow_distance}(a), we plot the minimum distance
between the vesicles as a function of time for various Hamaker
constants.  The red curves correspond to Hamaker constants that are too
small to bind the vesicles into a doublet, and the blue curves
correspond to Hamaker constants that are sufficiently large to form a
doublet.

In Figure~\ref{fig:sflow_distance}(b), we plot the time required for the
doublet to make a complete revolution at a variety of Hamaker constants
and shear rates.  For a fixed Hamaker constant, as expected, the period
decreases for larger shear rates.  In addition, for a fixed shear rate,
the period decreases as the Hamaker constant increases, but the period
eventually plateaus.  The dynamics of these doublet have similar
behavior to a single rigid body undergoing a Jeffery orbit in a shear
flow.  Therefore, we define the effective aspect ratio
$\lambda_{\mathrm{eff}}$ which satisfies
\begin{align*}
  \frac{2\pi}{\chi}\left(\lambda + \lambda^{-1} \right) = p,
\end{align*}
where $p$ is the period of the doublet.  The effective aspect ratio is
the aspect ratio of an ellipse in a shear flow that is undergoing a
Jeffery orbit with period $p$.  For the Hamaker constant $\mathcal{H} =
2$, the shear rates, periods, and effective aspect ratio are summarized
in Table~\ref{tbl:aspectRatio}.  Since the effective aspect ratio is
comparable for all three shear rates, this indicates that the dynamics
of a vesicle doublet in a shear flow resembles a rigid body undergoing a
Jeffery orbit.
\begin{table}[htp]
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\chi$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
  0.50 & 38.06 & 2.92 \\
  0.75 & 24.81 & 2.85 \\
  1.00 & 19.47 & 3.00 
\end{tabular}
\caption{\label{tbl:aspectRatio} The shear rate, period, and effective
aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
Hamaker constant $\mathcal{H} = 2$, and separation distance $\delta =
0.4$.  The effective aspect ratios are comparable for all three shear
rates.}
\end{table}

### 2019-06-25 vesicle_code/docs/adhesion/revisions/reviewer2.tex
worked on revisions

\noindent
\comment{Fig 12: the authors did not comment the evolution of the
frequency of distance oscillations in doublets when the Hamaker constant
is varied. Can it be compared to the natural rotation frequency of the
shear flow $\chi/2$? Does a strongly adhesive doublet tend to behave as
a tumbling rigid object following something similar to Jeffery orbits?}
\begin{itemize}
  \item rebuttal
\end{itemize}

>>>>

\noindent
\comment{Fig 12: the authors did not comment the evolution of the
frequency of distance oscillations in doublets when the Hamaker constant
is varied. Can it be compared to the natural rotation frequency of the
shear flow $\chi/2$? Does a strongly adhesive doublet tend to behave as
a tumbling rigid object following something similar to Jeffery orbits?}
\begin{itemize}
  \item We now report the period of the doublets at three different
    shear rates and at a variety of Hamaker constants.

  \item For each of the shear rates and the largest Hamaker constant we
    consider, we compute an effective aspect ratio which is the aspect
    ratio of a rigid body ellipse that would undergo the same period in
    the same shear flow.  The results indicate that the effective aspect
    ratio is independent of the shear rate, and this suggests that the
    dynamics of the doublet has similar properties to a rigid body
    undergoing a Jeffery orbit. 
\end{itemize}
